Gravitational Lens Modeling in a Citizen Science Context

### 2014-08-05 text/ms.tex
table to 3 col layout

\begin{table}\centering\begin{tabular}{lr}\hline
    Total & 119 (100\%)\\
\hline
    errors in image locations  & 9 (8\%)\\
    errors in image parities or time ordering & 49 (41\%) \\
\hline
    inaccurate image placement over an arc & 21 (18\%) \\
    identified two images of four & 5 (4\%) \\
    identified two nearby images as one & 3 (3\%) \\
    missed faint images & 1 (1\%) \\
    proposed too many images & 1 (1\%) \\
    modelled a three-image arc as one image & 4 (3\%) \\
    modelled one image as a three-image arc & 5 (4\%) \\
    swapped minimum and saddle in double  & 2 (2\%) \\
    swapped minima and saddles in quad & 38 (32\%)\\
    swapped early and late saddles in a quad & 7 (6\%) \\
\hline
\end{tabular}
\caption{Table of image-identification errors and the number of models
  containing each.  A model can contain more than one type of error.}
\label{tab:stats}
\end{table}

>>>>

\begin{table}\centering\begin{tabular}{lrr}\hline
    Total & 119 &(100\%)\\
\hline
    errors in image locations  & 9 &(8\%)\\
    errors in image parities or time ordering & 49 &(41\%) \\
\hline
    inaccurate image placement over an arc & 21 &(18\%) \\
    identified two images of four & 5 &(4\%) \\
    identified two nearby images as one & 3 &(3\%) \\
    missed faint images & 1 &(1\%) \\
    proposed too many images & 1 &(1\%) \\
    modelled a three-image arc as one image & 4 &(3\%) \\
    modelled one image as a three-image arc & 5 &(4\%) \\
    swapped minimum and saddle in double  & 2 &(2\%) \\
    swapped minima and saddles in quad & 38 &(32\%)\\
    swapped early and late saddles in a quad & 7 &(6\%) \\
\hline
\end{tabular}
\caption{Table of image-identification errors and the number of models
  containing each.  A model can contain more than one type of error.}
\label{tab:stats}
\end{table}
